---
title: "Portfolio Analysis Report"
author: "Ryan Lovelock"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning =  FALSE, fig.width=12, fig.height=6)
```


``` {r data work, echo = FALSE, include = FALSE, message = FALSE}
# Set working directory
#setwd("xx")

# install.packages("readxl", "magrittr", "dplyr", "tidyr", "lubridate", "knitr", "ggplot2", "kableExtra")

# Load necessary libraries
library(readxl)
library(magrittr)
library(dplyr)
library(tidyr)
library(lubridate)
library(knitr)
library(ggplot2)
library(kableExtra)

# Read data from specified excel file and sheet
data <- read_excel('data.xlsx', sheet = 1, col_names = TRUE)

#Convert refdate to Date format
data$refdate <- as.Date(data$refdate)

# Rename columns to make them more readable
data <- data %>%
  rename(Date = refdate, `Portfolio Weight (%)` = `Weight (%)`, Beta = `Beta (Relative to Benchmark)`, `Market Cap ($)` = `Market Capitalization (USD)`, `Price ($)` = `Price(USD)`,
         `Environmental Score` = `Overall ESG Environmental Score`, `Social Score` = `Overall ESG Social Score`,
         `Governance Score` = `Overall ESG Governance Score`, `GICS Sector` = GICS_sector, `Cont. TE (%)` = `%Contribution to Tracking Error`,
         `Cont. Total Risk (%)` = `%Contribution to Total Risk`)

# Convert other columns to their required formats
data <- data %>%
  mutate(
    `Portfolio Weight (%)` = round(as.numeric(`Portfolio Weight (%)`*100),2),
    `Active Weight (%)` = round(as.numeric(`Active Weight (%)`*100),2),
    `Total Risk` = round(as.numeric(`Total Risk`),2),
    `Beta` = round(as.numeric(`Beta`),2),
    `Market Cap ($)` = round(as.numeric(`Market Cap ($)`),2),
    `Cont. TE (%)` = round(as.numeric(`Cont. TE (%)`*100),2),
    `Cont. Total Risk (%)` = round(as.numeric(`Cont. Total Risk (%)`*100),2),
    `Overall ESG Score` = as.numeric(`Overall ESG Score`),
    `Environmental Score` = as.numeric(`Environmental Score`),
    `Social Score` = as.numeric(`Social Score`),
    `Governance Score` = as.numeric(`Governance Score`)
  )

# Categorise assets into Cash, FX and Equity using the Market Cap column
data <- data %>%
  mutate(`Asset Type` = case_when(
    `Market Cap ($)` == 0 ~ 'Cash',
    is.na(`Market Cap ($)`) ~ 'FX',
    TRUE ~ 'Equity'
  ))

# Categorise assets into market cap categories
data <- data %>% 
  mutate(`Market Cap Category ($)` = case_when(
    `Market Cap ($)` < 300000000 ~ "<300mn",
    `Market Cap ($)` >= 300000000 & `Market Cap ($)`< 2000000000 ~ "300mn-2bn",
    `Market Cap ($)` >= 2000000000 & `Market Cap ($)`< 6000000000 ~ "2bn-6bn",
    `Market Cap ($)` >= 6000000000 & `Market Cap ($)`< 10000000000 ~ "6bn-10bn",
    `Market Cap ($)` > 10000000000 ~ ">10bn", 
    TRUE ~ NA_character_
  ))

# Categorise assets into ESG categories
data <- data %>%
  mutate(`ESG Category` = case_when(
    `Overall ESG Score` < 3 ~ 'Laggard',
    `Overall ESG Score` >= 3 & `Overall ESG Score` < 7 ~ 'Average',
    `Overall ESG Score` >= 7 ~ 'Leader',
    TRUE ~ NA_character_
  ))

# Remove 31st December as this is a weekend date and the data does not look accurate 
ts_data <- data %>% filter(Date != '2023-12-31')
# Split out latest date to get current portfolio shape
latest_data <- data %>% filter(Date == '2023-12-29')

# Use the latest data to calculate top-level risk stats 
portfolio_te <- round(sqrt(sum(((latest_data$`Active Weight (%)`/100)^2)*(latest_data$`Total Risk`^2))),2)
portfolio_beta <- round(weighted.mean(latest_data$`Beta`, w = latest_data$`Portfolio Weight (%)`, na.rm = TRUE),2)
portfolio_esg <- round(weighted.mean(latest_data$`Overall ESG Score`, w = latest_data$`Portfolio Weight (%)`, na.rm = TRUE),2)
n_holdings <- round(nrow(latest_data %>% filter(`Asset Type` == 'Equity')),0)
cash <- round(sum(latest_data %>% filter(`Asset Type` == "Cash") %>% pull(`Portfolio Weight (%)`), na.rm = TRUE),2)
fx <- round(sum(latest_data %>% filter(`Asset Type` == "FX") %>% pull(`Portfolio Weight (%)`), na.rm = TRUE),2)
fund_vol <- round(sum(latest_data$`Total Risk`, na.rm = TRUE)/100, 2)

# Create table to summarise top-level risk stats
portfolio_stats <- data.frame(Metric = c("Portfolio Tracking Error %", "Portfolio Beta", "Portfolio ESG Score", "Number of Holdings", "Cash %", "Fund Volatility %", "FX %"),
                              Value = c(portfolio_te,  portfolio_beta, portfolio_esg, n_holdings, cash, fund_vol, fx))

## Current portfolio shape 
# Calculate the sum of contributions
total_contribution <- sum(latest_data$`Cont. TE (%)`)

# Calculate the normalisation factor
normalisation_factor <- total_contribution / 100

# Normalise the contributions
latest_data <- latest_data %>%
  mutate(`Normalised Contribution to TE (%)` = `Cont. TE (%)` / normalisation_factor)

# Create new column showing normalised tracking error contributions that = 100
latest_data$`Normalised Contribution to TE (%)` <- round(latest_data$`Normalised Contribution to TE (%)`,2)

# top 10 contributors to tracking error (relative to benchmark)
top_te_contributors <- latest_data %>% 
  arrange(desc(`Normalised Contribution to TE (%)`)) %>% 
  select(`Asset Name`, 
         `Portfolio Weight (%)`, 
         `Active Weight (%)`, 
         `Normalised Contribution to TE (%)`,
         `Beta`,
         `GICS Sector`,
         `Country`) %>%
  head(10)

# Find totals of these columns to bind to table
totals_te <- top_te_contributors %>%
  summarise(
    `Asset Name` = "Total",
    `Portfolio Weight (%)` = sum(`Portfolio Weight (%)`, na.rm = TRUE),
    `Active Weight (%)` = sum(`Active Weight (%)`, na.rm = TRUE),
    `Normalised Contribution to TE (%)` = sum(`Normalised Contribution to TE (%)`, na.rm = TRUE),
    `Beta` = NA,  # Not summing Beta, as it doesn't make sense to sum it
    `GICS Sector` = NA,
    `Country` = NA
  )

# Bind the total row to the existing data frame
top_te_contributors_with_total <- bind_rows(top_te_contributors, totals_te)


# Top 10 contributors to total risk (absolute)
top_risk_contributors <- latest_data %>% 
  arrange(desc(`Cont. Total Risk (%)`)) %>% 
  select(`Asset Name`, 
         `Portfolio Weight (%)`, 
         `Active Weight (%)`, 
         `Cont. Total Risk (%)`,
         `Beta`,
         `GICS Sector`,
         `Country`) %>%
  head(10)

totals <- top_risk_contributors %>%
  summarise(
    `Asset Name` = "Total",
    `Portfolio Weight (%)` = sum(`Portfolio Weight (%)`, na.rm = TRUE),
    `Active Weight (%)` = sum(`Active Weight (%)`, na.rm = TRUE),
    `Cont. Total Risk (%)` = sum(`Cont. Total Risk (%)`, na.rm = TRUE),
    `Beta` = NA,  # Not summing Beta, as it doesn't make sense to sum it
    `GICS Sector` = NA,
    `Country` = NA
  )

# Bind the total row to the existing data frame
top_risk_contributors_with_total <- bind_rows(top_risk_contributors, totals)


## Sector breakdown
sector_breakdown <- latest_data %>% 
  filter(`Asset Type` == 'Equity') %>%
  group_by(`GICS Sector`) %>% 
  summarise(`Port Stocks` = n(), 
            `Portfolio Weight (%)` = sum(`Portfolio Weight (%)`, na.rm = TRUE),
            `Active Weight (%)` = sum(`Active Weight (%)`, na.rm = TRUE),
            `Normalised Contribution to TE (%)` = sum(`Normalised Contribution to TE (%)`, na.rm = TRUE)) %>%
  arrange(desc(`Normalised Contribution to TE (%)`))



## Country breakdown
country_breakdown <- latest_data %>%
  filter(`Asset Type` == 'Equity') %>% 
  group_by(Country) %>% 
  summarise(`Port Stocks` = n(), 
            `Portfolio Weight (%)` = sum(`Portfolio Weight (%)`, na.rm = TRUE),
            `Active Weight (%)` = sum(`Active Weight (%)`, na.rm = TRUE),
            `Normalised Contribution to TE (%)` = sum(`Normalised Contribution to TE (%)`, na.rm = TRUE)) %>%
  arrange(desc(`Normalised Contribution to TE (%)`))



## Market cap breakdown
mc_breakdown <- latest_data %>% 
  filter(`Asset Type` == 'Equity') %>%
  group_by(`Market Cap Category ($)`) %>% 
  summarise(`Port Stocks` = n(), 
            `Portfolio Weight (%)` = sum(`Portfolio Weight (%)`, na.rm = TRUE),
            `Active Weight (%)` = sum(`Active Weight (%)`, na.rm = TRUE),
            `Normalised Contribution to TE (%)` = sum(`Normalised Contribution to TE (%)`, na.rm = TRUE)) %>%
  arrange(desc(`Normalised Contribution to TE (%)`))

## ESG scores
top10_esg <- latest_data %>% 
  arrange(desc(`Overall ESG Score`)) %>%
  select(`Asset Name`, `Overall ESG Score`, `Environmental Score`, `Social Score`, `Governance Score`, `Active Weight (%)`, `Normalised Contribution to TE (%)`,  `GICS Sector`, Country) %>%
  head(10)

bottom10_esg <- latest_data %>% 
  arrange(`Overall ESG Score`) %>%
  select(`Asset Name`, `Overall ESG Score`, `Environmental Score`, `Social Score`, `Governance Score`, `Active Weight (%)`, `Normalised Contribution to TE (%)`,  `GICS Sector`, Country) %>%
  head(10)

## Time series analysis

# Filter for end of month data
month_end_data <- ts_data %>%
  group_by(year = year(Date), month = month(Date)) %>%
  filter(Date == max(Date)) %>%
  ungroup() %>%
  select(-year, -month)

## Tracking error over time
te_ot <- ts_data %>% 
  filter(!is.na(Date)) %>%
  group_by(Date) %>%
  summarise(Tracking_Error = sqrt(sum(((`Active Weight (%)`/100)^2)*(`Total Risk`^2))))

## Beta over time
beta_ot <- ts_data %>% 
  filter(!is.na(Date)) %>%
  group_by(Date) %>%
  summarise(Beta = weighted.mean(`Beta`, w = `Portfolio Weight (%)`, na.rm = TRUE))

## Fund vol over time
fundvol_ot <- ts_data %>% 
  filter(!is.na(Date)) %>%
  group_by(Date) %>%
  summarise(FundVol = sum(`Total Risk`, na.rm = TRUE)/100)

# ESG breakdown 
# Calculate weighted average ESG scores for each date
weighted_esg_scores <- month_end_data %>%
  group_by(Date) %>%
  summarise(
    `E Score` = sum(`Portfolio Weight (%)` * `Environmental Score`, na.rm = TRUE) / sum(`Portfolio Weight (%)`, na.rm = TRUE),
    `S Score` = sum(`Portfolio Weight (%)` * `Social Score`, na.rm = TRUE) / sum(`Portfolio Weight (%)`, na.rm = TRUE),
    `G Score` = sum(`Portfolio Weight (%)` * `Governance Score`, na.rm = TRUE) / sum(`Portfolio Weight (%)`, na.rm = TRUE),
    `Overall ESG Score` = sum(`Portfolio Weight (%)` * `Overall ESG Score`, na.rm = TRUE) / sum(`Portfolio Weight (%)`, na.rm = TRUE)
  )

# transform wide data to long to make graphing easier 
long_esg_scores <- weighted_esg_scores %>%
  pivot_longer(cols = contains("Score"), names_to = "ESG_Type", values_to = "Score")

## Weights of ESG brackets
category_weights <- month_end_data %>%
  group_by(Date, `ESG Category`) %>%
  summarise(total_weight = sum(`Portfolio Weight (%)`, na.rm = TRUE)) %>%
  ungroup()

# Performance over time 
# Filter for year to date figures, for equity positions and exclude health care as data doesnt look correct
perf_data <- ts_data %>% filter(`Asset Type` == 'Equity', Date >= "2023-01-01", `GICS Sector` != 'Health Care')

# Calculate the weighted average price of the portfolio over time
# Group the data by Date and compute the weighted average price
fund_performance <- perf_data %>%
  group_by(Date) %>%
  summarise(weighted_avg_price = sum(`Portfolio Weight (%)` * `Price ($)`, na.rm = TRUE) / sum(`Portfolio Weight (%)`, na.rm = TRUE)
            )
# Normalise the weighted average price to create an index
# The index is set to 100 at the first date
fund_performance <- fund_performance %>% 
  mutate(Index = (weighted_avg_price / first(weighted_avg_price)) *100)

# Sector performance over time
# Calculate the weighted average price of the portfolio over time
# Group the data by Date and sector to compute the weighted average price
index_sector_performance <- perf_data %>%
    group_by(Date, `GICS Sector`) %>%
    summarise(sector_weighted_avg_price = sum(`Portfolio Weight (%)` * `Price ($)`, na.rm = TRUE) / sum(`Portfolio Weight (%)`, na.rm = TRUE)
    ) %>%
    ungroup()

# Normalise the weighted average price to create an index
# The index is set to 100 at the first date
index_sector_performance <- index_sector_performance %>%
  group_by(`GICS Sector`) %>%
  mutate(Index = (sector_weighted_avg_price / first(sector_weighted_avg_price)) *100) %>%
           ungroup()
```

This report aims to identify and analyse the key drivers of portfolio risk, performance, and ESG trends within an equity portfolio. The table below presents the top-level risk statistics as of the latest date, December 29, 2023.

## Top Level Risk Statistics

The table below indicates that the portfolio has a tracking error (TE) of 5.27%, suggesting that the fund's returns may deviate moderately from the benchmark's returns. This level of tracking error implies that the portfolio manager is engaging in more active management strategies, potentially seeking higher returns through active bets relative to the benchmark. The portfolio's beta is 1.08, indicating that it is slightly more volatile than its benchmark. The portfolio currently holds 36 open equity positions and includes various currency holdings. The most recent measure of the fund's volatility is 15.24%, reflecting the degree of variation in the portfolio's returns over a specific period.

``` {r top table, echo =FALSE}
kable(portfolio_stats, caption = "Top Level Risk Statistics") %>%
  kable_styling(font_size = 9)
```

## Top 10 Contributors to Risk {.tabset}
The tables below present both relative and absolute contributions to risk within the portfolio. In the tracking error table, the risk contributions have been normalised to display active positions as a percentage of the total tracking error. The top 10 contributors to tracking error account for 50% of the total tracking error, indicating that the fund is well diversified. The leading contributors to tracking error are Kingdee International, Silergy Corporation and Meituan. All 3 of these positions also have very high betas relative to the benchmark. 

When examining the contributors to absolute portfolio risk, Taiwan Semiconductor Manufacturing Company (TSMC) and Samsung Electronics emerge as the largest contributors. The top 10 contributors to absolute risk collectively account for 53% of the total portfolio risk.

Note: the data used doesn't include full benchmark data or returns data and so the tracking error calculations are estimates and based on various assumptions. 

### Tracking Error
``` {r top 10 te, echo = FALSE}
# Display the table with kable
kable(top_te_contributors_with_total, caption = "Largest Contr. TE - Top 10") %>%
  kable_styling(font_size = 9)
```

### Total Portfolio Risk
``` {r top risk, echo = FALSE}
kable(top_risk_contributors_with_total, caption = "Largest Contr. Total Risk - Top 10") %>%
  kable_styling(font_size = 9)
```

## Tracking Error - Sector Breakdown {.tabset}

This section presents the sector contributions to tracking error alongside their respective active weights. Financials contribute 32% to the tracking error, with an overweight position of 29%. Information Technology follows closely, contributing 29% to the tracking error, with an overweight position of 19%.

The table on the second tab provides a detailed tabular representation of this data.

Note: Active weights are depicted as orange dots on the right-hand side (RHS), while the contributions to tracking error are shown as purple bars on the left-hand side (LHS).

### Plot
```{r sector bar, echo=FALSE}
ggplot(sector_breakdown, aes(x=reorder(`GICS Sector`, -`Normalised Contribution to TE (%)`))) +
  geom_bar(aes(y = `Normalised Contribution to TE (%)`), stat = "identity", fill = "#4432a8") +
  geom_point(aes(y = `Active Weight (%)` * max(`Normalised Contribution to TE (%)`)/max(`Active Weight (%)`)), color = '#D55E00', size = 3) +
  scale_y_continuous(
    name = "Contribution to Tracking Error (%)",
    sec.axis = sec_axis(~ . * max(sector_breakdown$`Active Weight (%)`) / max(sector_breakdown$`Normalised Contribution to TE (%)`), name = "Active Weight (%)")
  ) +
  theme_minimal() +
  theme(legend.position = 'bottom') +
  xlab("Sector") +
  ggtitle("Portfolio Sector Breakdown") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Table
```{r sector table, echo=FALSE}
kable(sector_breakdown) %>%
  kable_styling(font_size = 9)
```

## Tracking Error - Country Breakdown {.tabset}
Below is the analysis of the country breakdown for tracking error contribution. The highest contributions are from Hong Kong, Taiwan, China, and the USA, all of which have significant overweight positions in the fund. Another notable country is India, which has a substantial overweight of nearly 12%, yet it contributes only 6% to the tracking error.

### Plot
``` {r country bar, echo = FALSE}
ggplot(country_breakdown, aes(x=reorder(`Country`, -`Normalised Contribution to TE (%)`))) +
  geom_bar(aes(y = `Normalised Contribution to TE (%)`), stat = "identity", fill = "#4432a8") +
  geom_point(aes(y = `Active Weight (%)` * max(`Normalised Contribution to TE (%)`)/max(`Active Weight (%)`)), color = '#D55E00', size = 3) +
  scale_y_continuous(
    name = "Contribution to Tracking Error (%)",
    sec.axis = sec_axis(~ . * max(country_breakdown$`Active Weight (%)`) / max(country_breakdown$`Normalised Contribution to TE (%)`), name = "Active Weight (%)")
  ) +
  theme_minimal() +
  theme(legend.position = 'bottom')+
  xlab("Country") +
  ggtitle("Portfolio Country Breakdown") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Table
``` {r country table, echo = FALSE}
kable(country_breakdown) %>%
  kable_styling(font_size = 9)
```


## Tracking Error - Market-cap Breakdown {.tabset}
The chart below illustrates the breakdown of market capitalisation in relation to tracking error contributions. Companies with a market capitalization exceeding \$10 billion make the most significant contribution, accounting for 72% of the total tracking error, with an active weight close to 61%. Mid-cap companies, with market capitalisations ranging from \$6 billion to \$10 billion, contribute approximately 17% to the tracking error. Smaller companies, with market capitalisations below $6 billion, contribute the remaining 10%.

### Plot
``` {r mc bar, echo = FALSE}
ggplot(mc_breakdown, aes(x=reorder(`Market Cap Category ($)`, -`Normalised Contribution to TE (%)`))) +
  geom_bar(aes(y = `Normalised Contribution to TE (%)`), stat = "identity", fill = "#4432a8") +
  geom_point(aes(y = `Active Weight (%)` * max(`Normalised Contribution to TE (%)`)/max(`Active Weight (%)`)), color = '#D55E00', size = 3) +
  scale_y_continuous(
    name = "Contribution to Tracking Error (%)",
    sec.axis = sec_axis(~ . * max(mc_breakdown$`Active Weight (%)`) / max(mc_breakdown$`Normalised Contribution to TE (%)`), name = "Active Weight (%)")
  ) +
  theme_minimal() +
  theme(legend.position = 'bottom') +
  xlab("Market Cap") +
  ggtitle("Portfolio Market Cap Breakdown") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Table 
``` {r mc table, echo = FALSE}
kable(mc_breakdown) %>%
  kable_styling(font_size = 9)
```


## ESG Scores by Security {.tabset}
The tables below display the top 10 and bottom 10 ESG-rated stocks held within the portfolio, along with their respective weights and contributions to tracking error. Companies such as TSMC, Samsung Electronics, Shenzhen Mindray, and Voltronic have very high ESG scores, indicating significant investments in sustainability practices.

Conversely, Leeno Industrial, East Money, and Sea Ltd have very low ESG scores, which negatively impact the average ESG score of the portfolio. Depending on the SFDR categorisation of this fund, the manager should consider removing these stocks, especially if they also contribute poorly to performance.


Note: The accuracy of this data is uncertain, and it should be supplemented with additional sources or replaced with more comprehensive data to enable a thorough analysis.

### Top 10
``` {r esgt, echo = FALSE}
kable(top10_esg, caption = "Top 10 ESG Scores") %>%
  kable_styling(font_size = 9)
```

### Bottom 10
``` {r esgb, echo = FALSE}
kable(bottom10_esg, caption = "Bottom 10 ESG Scores") %>%
  kable_styling(font_size = 9)
```


## Risk Stats Over Time {.tabset}
The tabs below present key risk statistics over time. Tracking Error experienced a significant decline at the end of 2022, dropping from 6.5% to 5.8%, and has continued to decrease gradually over the past year.

The fund's beta has generally remained above 1, with occasional dips below 1 throughout the year. These fluctuations are likely attributable to daily market movements.

Fund volatility has remained relatively stable over the past year. However, the most recent data indicates that the fund is currently experiencing its lowest volatility in 2023.

### Tracking Error Over Time
``` {r teot, echo = FALSE}
ggplot(te_ot, aes( x= Date, y = Tracking_Error)) +
  geom_line(color = '#4432a8', size = 1) +
  theme_minimal() +
  xlab("Date") +
  ylab("Tracking Error %") +
  ggtitle("Tracking Error Over Time") +
  expand_limits(y=0)
```

### Beta Over Time
``` {r bot, echo = FALSE}
ggplot(beta_ot, aes( x= Date, y = Beta)) +
  geom_line(color = '#4432a8', size = 1) +
  theme_minimal() +
  xlab("Date") +
  ylab("Beta") +
  ggtitle("Beta Over Time") +
  expand_limits(y=0)
```

### Fund Volatility Over Time
``` {r fvot, echo = FALSE}
ggplot(fundvol_ot, aes( x= Date, y = FundVol)) +
  geom_line(color = '#4432a8', size =1) +
  theme_minimal() +
  xlab("Date") +
  ylab("Fund Volatility %") +
  ggtitle("Fund Volatility Over Time") +
  expand_limits(y=0)
```

## ESG Over Time
Overall ESG scores and their respective breakdowns have remained relatively stable over time, indicating that the companies held in this portfolio have neither significantly improved nor deteriorated in the metrics that comprise each score.

Note: To provide a more comprehensive analysis, this data should be extended to include additional metrics from a range of providers.

``` {r esgot, echo = FALSE}
ggplot(long_esg_scores, aes(x = Date, y = Score, color = ESG_Type)) +
  geom_line(size = 1) +
  theme_minimal() +
  theme(legend.position = 'bottom')+
  xlab("Date") +
  ylab("Weighted ESG Score") +
  ggtitle("Weighted ESG Scores Over Time") +
  scale_color_manual(values = c("E Score" = '#4432a8', "S Score" = '#D55E00', "G Score" = '#184f1a', "Overall ESG Score" = '#54180e'),
                     breaks = c("Overall ESG Score", "E Score", "S Score", "G Score")) +
  expand_limits(y = 0)
```

The chart below illustrates the shifts in portfolio weightings across ESG categories. The "Leader" category (companies with ESG scores greater than 7) has been gradually increasing throughout the year, while the "Average" (ESG score between 3 and 7) category has shown a corresponding decline. This trend indicates that the fund is progressively allocating more weight to higher ESG-rated stocks. 

``` {r esgcatot, echo = FALSE}
ggplot(category_weights, aes(x = Date, y = total_weight, color = `ESG Category`)) +
  geom_line(size = 1) +
  theme_minimal() +
  theme(legend.position = 'bottom') +
  xlab("Date") +
  ylab("Total Portfolio Weight (%)") +
  ggtitle("Changes in Portfolio Weights by ESG Category Over Time") +
  scale_color_manual(
    values = c("Laggard" = '#4432a8', "Average" = '#D55E00', "Leader" = '#009E73'),
    name = "ESG Category"
  ) +
  expand_limits(y = 0)
```

## Performance Over Time
The chart below depicts performance over time, with the initial data point indexed to 100. The fund has experienced strong performance since the beginning of the year, with a slight plateau observed between June and November, followed by a continued positive trajectory up to the most recent data point.

``` {r perfot, echo = FALSE}
ggplot(fund_performance, aes(x = Date, y =Index)) +
  geom_line(color = '#4432a8') +
  geom_point(color = '#D55E00') +
  ggtitle("Fund Performance Over Time") +
  theme_minimal() +
  scale_x_date(date_breaks = "1 month", date_labels = "%b %Y")
```

This chart illustrates the performance over time, segmented by sector. Information Technology has demonstrated promising growth throughout the year, with a significant surge between February and March, maintaining that elevated level for the remainder of the year. Other notable sectors include Consumer Discretionary, which has exhibited strong recent performance, and Communication Services, which began the year underperforming but has rebounded in the second half of the year.

``` {r secperfot, echo = FALSE}
ggplot(index_sector_performance, aes(x = Date, y =Index, color = `GICS Sector`)) +
  geom_line(size = 1) +
  geom_point() +
  theme_minimal() +
  ggtitle("Fund Performance Over Time - Sector Breakdown") +
  theme(legend.position = 'bottom') + 
  scale_x_date(date_breaks = "1 month", date_labels = "%b %Y")
```

## Further Analysis
The data used for this analysis was somewhat limited and may contain inaccuracies in certain areas. To enhance the robustness and reliability of our findings, it is essential to integrate additional data sources to establish a more comprehensive dataset and verify the quality of our existing data. Once this is achieved, further analysis could include:

1. Factor-Based and Brinson Attribution: Conducting factor-based and Brinson attribution analyses to understand the drivers of performance over time.\
2. Detailed Tracking Error Analysis: Breaking down tracking error into factor and specific components to gain deeper insights into the sources of risk.\
3. ESG Score Contribution: Analysing how stocks with different ESG scores contribute to overall portfolio performance.





